\documentclass[a4paper,6pt]{article}
\usepackage{tabularx}
\usepackage[left=0.5cm,right=1cm,bottom=1.5cm,top=1cm,bindingoffset=0.5cm]{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage{xcolor}
\definecolor{mygray}{gray}{0.4}
\usepackage[sfdefault,light]{FiraSans} %% option 'sfdefault' activates Fira Sans as the default text font
\usepackage[T1]{fontenc}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}

% Margin adjustments
%\addtolength{\oddsidemargin}{-1.5in}
%\addtolength{\evensidemargin}{-1.5in}
% Sans serif fontface
% \renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}
  {\normalfont\scshape}{\thesection}{1em}{}

\setlength{\parindent}{0px}
\addtolength{\textheight}{1.0in}
\linespread{0}
\setlength{\parskip}{0.3ex}

\setlist{nolistsep}

\begin{document}
\begin{center}
\Large \textbf{SHREYAS PAPINWAR}


\end{center}
\begin{tabularx}{\textwidth}{X r}
	https://shreyasp.me &  spapinwar@gmail.com \vspace{2px} \\
	https://github.com/shreyaspapi & +91 98345 47140 
\end{tabularx}


\vspace{-9px}
\section*{Programming Skills}
\vspace{-8px}
\hrule
\vspace{8px}
\begin{itemize}
	\item \hspace{3px} \textbf{Programming}: \small Swift (SwiftUI, SpriteKit), Python, JavaScript, TypeScript
\normalsize
\vspace{2px}
	\item \hspace{3px} \textbf{Frameworks}: \small Node, Angular, React Native, Flask, Gatsby, Sanity
\normalsize
\vspace{2px}
	\item \hspace{3px} \textbf{Platforms}: \small Google Cloud Platform (GCP), Amazon Web Services (AWS), Heroku
\normalsize
\vspace{2px}
	\item \hspace{3px} \textbf{Technologies}: \small Docker, Jenkins, Travis, CI/CD, Git, MongoDB
\normalsize
\end{itemize}


\vspace{-9px}
\section*{Experience}
\vspace{-8px}
\hrule



\vspace{7px}
\begin{tabularx}{\textwidth}{X r}
	\large{\textbf{\href{https://play.google.com/store/apps/details?id=com.Newsg8r}{\textcolor{black}{\textbf{Newsg8r}}}}} \vspace{1px} & \\
	\textit{\small Lead Developer}& \textit{March 2020 - December 2020} \\
\end{tabularx}

\small
\begin{itemize}
	\itemsep0em
	\item Managed and deployed \textcolor{mygray}{\textbf{Node API's}} that helped create content management system (CMS).
	\item Managed and Configured \textcolor{mygray}{\textbf{Jenkins}} for CI/CD of the web app developed in \textcolor{mygray}{\textbf{Angular 10}} and \textcolor{mygray}{\textbf{NodeJS}}.
	\item Used and configured codemagic for \textcolor{mygray}{\textbf{Flutter}} app (iOS/Android) CI/CD.
	\item Developed and deployed both web app and mobile app (Android and iOS) using \textcolor{mygray}{\textbf{Angular}} and \textcolor{mygray}{\textbf{Flutter}}. \href{https://play.google.com/store/apps/details?id=com.Newsg8r}{\textcolor{blue}{\textbf{\underline{Play Store}}}}
	\item Converted micro services to AWS Lambda which reduced the cost of AWS by \textcolor{mygray}{\textbf{30 percent}}.
\end{itemize}
\normalsize


\vspace{7px}
\begin{tabularx}{\textwidth}{X r}
	\large{\textbf{Google Summer of Code}} \vspace{1px} & \\
	\textit{\small Fedora (Redhat)}& \textit{May 2020 - August 2020} \\
\end{tabularx}

\small
\begin{itemize}
	\itemsep0em
	\item Implemented Gitlab support for open source project Packit by contributing to \href{https://github.com/packit/packit/pulls/shreyaspapi}{\textcolor{blue}{\textbf{\underline{Packit}}}}, \href{https://github.com/packit/packit-service/pulls/shreyaspapi}{\textcolor{blue}{\textbf{\underline{Packit-Service}}}}, and \href{https://github.com/packit/ogr/pulls/shreyaspapi}{\textcolor{blue}{\textbf{\underline{Ogr}}}} repositories.
	\item Researched on the ways to implement Gitlab support with packit. \href{https://github.com/packit/research/tree/master/gitlab_integration}{\textcolor{blue}{\textbf{\underline{link}}}}
	\item Final submission blog of the work done to integrate with Gitlab. \href{https://shreyaspapi.medium.com/gsoc-gitlab-support-in-packit-service-fedora-54df1024b176}{\textcolor{blue}{\textbf{\underline{link}}}}
\end{itemize}
\normalsize

\vspace{4px}
\begin{tabularx}{\textwidth}{X r}
	\large{\textbf{Flavazo}} \vspace{4px} & \\
	\textit{\small Software Developer} & \textit{July 2019 - February 2020} \\
\end{tabularx}

\small
\begin{itemize}
	\itemsep0em
	\item Used \textcolor{mygray}{\textbf{NodeJS}} and \textcolor{mygray}{\textbf{Express}} framework to build server side logic and applied with \textcolor{mygray}{\textbf{middleware}} to handle HTTP requests.
	\item Managed and deployed node API’s using AWS elastic beanstack and Travis CI.
    \item Developed add to cart and payment feature using RazerPay in React Native app.
    \item Decreased the load time of the react native app by 30 percent.
    \item Deployed the Android and iOS app to \href{https://play.google.com/store/apps/details?id=com.flavazo.user}{\textcolor{blue}{\textbf{\underline{Play Store}}}}.
\end{itemize}

\normalsize
\vspace{2px}
\begin{tabularx}{\textwidth}{X r}
	\textit{\small Machine Learning Intern}& \textit{April 2019 - June 2019} \\
\end{tabularx}

\small
\begin{itemize}
	\itemsep0em
	\item Built scraping scripts to get user reviews of different restaurants and user details using \textcolor{mygray}{\textbf{Python (Scrapy, Selenium)}}.
    \item Developed food recommendation system based on scraped restaurant user reviews.
    \item Built and deployed the back-end in \textcolor{mygray}{\textbf{NodeJS}} which recommended food and restaurants based on the \textcolor{mygray}{\textbf{user persona}}.
\end{itemize}


\vspace{6px}
\begin{tabularx}{\textwidth}{X r}
	\large{\textbf{Georgia Institute of Technology}} \vspace{2px} & \\
	\textit{\small Research Intern}& \textit{April 2018 - July 2018} \\
\end{tabularx}

\small
\begin{itemize}
	\itemsep0em
	\item Worked on parallel programming in JAVA, the main idea of the project was to work on self driving vehicle simulation.
	\item Responsible for building the web part of the project made using Python (Flask).
\end{itemize}



\vspace{-9px}
\section*{Leadership and achievements}
\vspace{-8px}
\hrule

\vspace{5px}
\begin{tabularx}{\textwidth}{X r}
	\large{\textbf{Microsoft Imagine Cup 2020}} \vspace{2px} & \\
	\textit{\small Finalist}& \textit{February 2020 - April 2020} \\
\end{tabularx}
\small
\begin{itemize}
	\itemsep0em
	\item One of the \textcolor{mygray}{\textbf{Top 10}} teams selected from \textcolor{mygray}{\textbf{Asia-Pacific APAC (18 countries)}}.
	\item Implemented face recognition using \textcolor{mygray}{\textbf{Azure’s Face API}} on web application made with Flask and React.
	\item Created mobile application in Xamarin which did the registration of people's face for public transportation.
	\item Final pitch for the Imagine Cup submission - \href{https://www.youtube.com/watch?v=RiNJscdLECA}{\textcolor{blue}{\textbf{\underline{link}}}}
\end{itemize}

\vspace{4px}
\begin{tabularx}{\textwidth}{X r}
	\large{\textbf{Smart India Hackathon (SIH) 2020}} \vspace{1px} & \\
	\textit{\small Hackathon Winner}& \textit{2020} \\
\end{tabularx}

\small
\begin{itemize}
	\itemsep0em
	\item Opportunity to show our project to the government and gain knowledge in the working of the industry.
	\item Got selected for Smart India Hackathon in under the transportation project where we improve the efficiency of the transportation.
\end{itemize}

\normalsize

\vspace{-9px}
\section*{Projects}
\vspace{-8px}
\hrule
\vspace{7px}
\begin{itemize}
    \item \textbf{The Corona App}: \small The app gives live updates of Covid-19 affected patients country wise, Data is taken from the covid19india.org and updated every 5 minutes. \href{https://www.producthunt.com/posts/the-f-cking-corona}{\textcolor{blue}{\textbf{\underline{Product Hunt}}}}
\normalsize
\vspace{2px}
	\item \textbf{Chess AI}: \small Created a chess reinforcement learning model using AlphaGo methods. Python (Flask, Tensorflow, Keras) \href{https://github.com/shreyaspapi/flask-chess-ai}{\textcolor{blue}{\textbf{\underline{Github}}}}

\normalsize
\end{itemize}

\section*{Education}
\vspace{-8px}
\hrule
\vspace{4px}
\begin{tabularx}{\textwidth}{X r}
	\textbf{Bennett University} & Delhi NCR, India \vspace{2px} \\
	\textit{\small Bachelor of Technology in Computer Science and Engineering } & \textit{2017 - Present} 
\end{tabularx}

\vspace{2px}

\begin{itemize}
    \item Awarded for best competitive programmer in 2018 and 2019 in University.
    \item Finalist in Entrepreneur's Camp at Bennett October 2018
    \item Represented university as a delegate in National Entrepreneurship conference 2019.
\end{itemize}

\end{document}
